### 2009-07-23 docs/FAQ/faq.tex
add the .dump_restart

@@

@@

   On some machines it does---Fortran 95 specifies that any local
   allocated arrays are automatically deallocated when a subroutine
   ends.  Fortran 90 does not do this.  On IBM machines, for instance,
   using {\tt xlf90} instead of {\tt xlf95} for MAESTRO will produce
   memory leaks.

@@

>>>>

\section{Compiling}

   On some machines it does---Fortran 95 specifies that any local
   allocated arrays are automatically deallocated when a subroutine
   ends.  Fortran 90 does not do this.  Most MAESTRO routines rely 
   on this Fortran 95 feature.

   On IBM machines, for instance, using {\tt xlf90} instead of {\tt
     xlf95} for MAESTRO will produce memory leaks.

\section{Running}

@@

\section{I/O}

@@

@@

\item {\em How can I force the code to output a plotfile at the next
   step?}

   In the output directory (where the code is running) do `{\tt touch
     .dump\_plotfile}'.  This will create an empty file called {\tt
     .dump\_plotfile}.  At the end of each step, if the code finds
   that file, it will output a plotfile.  Simply delete the file to
   restore the code to its normal plotfile behavior.
